Order-Adaptive Regularisation for Variational Optic Flow:\\Global, Local and in Between

### 2018-07-19 seminar_vof/paper/paper.tex
second order term mathized

\newcommand{\lam}{\lambda}
\newcommand{\trans}{\quad\bigg|\;}
\newcommand{\Trans}{\quad\Bigg|\;}
% matrix shortcut
\newcommand{\mat}[1]{\begin{pmatrix} #1 \end{pmatrix}}
% matrix shortcut with increased vertical spacing
\newcommand{\Mat}[1]{\begingroup
\renewcommand*{\arraystretch}{1.5}
\mat{#1}
\endgroup}
% matrix format but without braces (secretly a matrix)
\newcommand{\secretMat}[2][r]{\begin{matrix*}[#1] #2 \end{matrix*}}
% matrix format but without braces (secretly a matrix) with increased vertical spacing
\newcommand{\SecretMat}[2][r]{\begingroup
\renewcommand*{\arraystretch}{1.7}
\secretMat[#1]{#2}
\endgroup}
% shortcuts for df/dx stuff in derivative
\newcommand{\der}{\partial}
\newcommand{\deriv}[2]{\frac{\der #1}{\der #2}}
% make star '*' become \cdot (normal multiplication sign)
\mathcode`\*="8000
{\catcode`\*\active\gdef*{\cdot}}
\newcommand{\Real}{\mathbb{R}}
\newcommand{\flow}{\vec{u}}
\newcommand{\x}{\vec{x}}
\newcommand{\y}{\vec{y}}
\newcommand{\ev}{\vec{r}}
\newcommand{\aaux}{\vec{a}}
\newcommand{\baux}{\vec{b}}
\newcommand{\T}{^\top}
\newcommand{\argmin}{\mathop{\mathrm{argmin}}}
\newcommand{\charbonnier}{\psi_{\text{Ch}}}
\newcommand{\peronamalik}{\psi_{\text{PM}}}
\newcommand{\Rfirst}{R_{1\text{st}}}
\newcommand{\Rsecond}{R_{2\text{nd}}}

@@

In order to minimize the energy functional, an iterative update sheme is developed using the euler lagrange equation \cite{eulerlagrange}.

@@

To continue the discussion of the regularization tensor, lets state its definition first.
\begin{flalign}\label{eq:structuretensor}
\mathcal{S}_\Phi(\x) &= \bigintsss \omega(\tau)\Mat{\Phi_x(\x-\tau)^2 && \Phi_x(\x-\tau)\Phi_y(\x-\tau)\\\Phi_x(\x-\tau)\Phi_y(\x-\tau) && \Phi_y(\x-\tau)^2} \;d\tau
&&\\\label{eq:eigendecomp}
\mathcal{S}_\Phi &= Q \Lambda Q\T = \mat{\ev_1&\ev_2}\mat{\lam_1&0\\0&\lam_2}\mat{\ev_1\T\\ \ev_2\T}&&
\end{flalign}
The tensor is a convolution of a weighting function $\omega$ with a matrix.
The matrix is the outer product of the gradient of the selected image feature $\Phi$ which is calculated as $\nabla\Phi(\x)\nabla\Phi(\x)\T$.
For the structure tensor the image feature would be brightness $\Phi=I$, but as this is the generalization, $\Phi$ can be something else like the saturation value in HSV color space or luminance of CIE L*a*b*.
Using the eigendecomposition, the orthonormal eigenvectors $\ev_1$ and $\ev_2$ are obtained which summarize the gradient distribution in the neighborhood defined by the weighting function $\omega$.
If the weighting function was a Dirac delta $\omega = \delta$ the eigendecomposition of the tensor would yield the normalized gradient as first eigenvector.
\begin{flalign*}
&\int \delta(\tau) \nabla\Phi(\x-\tau)\nabla\Phi(\x-\tau)\T \;d\tau = \nabla\Phi(\x)\nabla\Phi(\x)\T&&
\\
&\nabla\Phi\nabla\Phi\T = \lambda_1*\ev_1\ev_1\T = \mat{\ev_1&\ev_2}\mat{\lambda_1&0\\0&0}\mat{\ev_1\T\\ \ev_2\T}&&
\end{flalign*}
Here the first eigenvalue is the squared length of the gradient $\lambda_1=|\nabla\Phi|^2$.
Of course this discussion only holds for Dirac delta as weighting function, for others like Gaussian, the eigenvectors cannot be factored in this way.

\subsection{Second Order Regularizer}
The second order term uses ...
\begin{flalign}
\Rsecond(\flow) =\;&\int_\Omega\; \inf_{\aaux,\baux}\big[\;S_2(\flow,\aaux,\baux) +\beta*S_\text{aux}(\aaux,\baux)\;\big] \;d\x
&&\\
S_2(\flow,\aaux,\baux) =\;& \peronamalik\Big( (\ev_1\T(\nabla u-\aaux))^2 + (\ev_1\T(\nabla v-\baux))^2 \Big)
&&\\
+\;&\charbonnier\Big( (\ev_2\T(\nabla u-\aaux))^2 + (\ev_2\T(\nabla v-\baux))^2 \Big)
&&\\
S_\text{aux}(\aaux,\baux) =\;&
&&
\end{flalign}

>>>>

\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}

\newcommand{\lam}{\lambda}
\newcommand{\trans}{\quad\bigg|\;}
\newcommand{\Trans}{\quad\Bigg|\;}
% matrix shortcut
\newcommand{\mat}[1]{\begin{pmatrix} #1 \end{pmatrix}}
% matrix shortcut with increased vertical spacing
\newcommand{\Mat}[1]{\begingroup
\renewcommand*{\arraystretch}{1.5}
\mat{#1}
\endgroup}
% matrix format but without braces (secretly a matrix)
\newcommand{\secretMat}[2][r]{\begin{matrix*}[#1] #2 \end{matrix*}}
% matrix format but without braces (secretly a matrix) with increased vertical spacing
\newcommand{\SecretMat}[2][r]{\begingroup
\renewcommand*{\arraystretch}{1.7}
\secretMat[#1]{#2}
\endgroup}
% shortcuts for df/dx stuff in derivative
\newcommand{\der}{\partial}
\newcommand{\deriv}[2]{\frac{\der #1}{\der #2}}
% make star '*' become \cdot (normal multiplication sign)
\mathcode`\*="8000
{\catcode`\*\active\gdef*{\cdot}}
\newcommand{\Real}{\mathbb{R}}
\newcommand{\flow}{\vec{u}}
\newcommand{\x}{\vec{x}}
\newcommand{\y}{\vec{y}}
\newcommand{\ev}{\vec{r}}
\newcommand{\aaux}{\vec{a}}
\newcommand{\baux}{\vec{b}}
\newcommand{\T}{^\top}
\newcommand{\argmin}{\mathop{\mathrm{argmin}}}
\newcommand{\charbonnier}{\psi_{\text{Ch}}}
\newcommand{\peronamalik}{\psi_{\text{PM}}}
\newcommand{\Rfirst}{R_{1\text{st}}}
\newcommand{\Rsecond}{R_{2\text{nd}}}
\newcommand{\jacob}{\mathcal{J}}

@@

In order to minimize the energy functional, an iterative update sheme is developed using the Euler-Lagrange equation \cite{mathforphysicists}.

@@

To continue the discussion of the regularization tensor, lets state its definition first.
\begin{flalign}\label{eq:structuretensor}
\mathcal{S}_{\Phi,\omega}(\x) &= \bigintsss \omega(\tau)\Mat{\Phi_x(\x-\tau)^2 && \Phi_x(\x-\tau)\Phi_y(\x-\tau)\\\Phi_x(\x-\tau)\Phi_y(\x-\tau) && \Phi_y(\x-\tau)^2} \;d\tau
&&\\\label{eq:eigendecomp}
\mathcal{S}_{\Phi,\omega}&= Q \Lambda Q\T = \mat{\ev_1&\ev_2}\mat{\lam_1&0\\0&\lam_2}\mat{\ev_1\T\\ \ev_2\T}&&
\end{flalign}
The tensor is a convolution of a weighting function $\omega$ with a matrix.
The matrix is the outer product of the gradient of the selected image feature $\Phi$ which is calculated as $\nabla\Phi(\x)\nabla\Phi(\x)\T$.
For the structure tensor the image feature would be brightness $\Phi=I$, but as this is the generalization, $\Phi$ can be something else like the saturation value in HSV color space or luminance of CIE L*a*b*.
Using the eigendecomposition (\cref{eq:eigendecomp}), the orthonormal eigenvectors $\ev_1$ and $\ev_2$ are obtained which summarize the gradient distribution in the neighborhood defined by the weighting function $\omega$.
If the weighting function was a Dirac delta $\omega = \delta$ the eigendecomposition of the tensor would yield the normalized gradient as first eigenvector.
\begin{flalign*}
\mathcal{S}_{\Phi,\delta}= \nabla\Phi\nabla\Phi\T = \lambda_1*\ev_1\ev_1\T = \mat{\ev_1&\ev_2}\mat{\lambda_1&0\\0&0}\mat{\ev_1\T\\ \ev_2\T}&&
\end{flalign*}
Here the first eigenvalue is the squared length of the gradient $\lambda_1=|\nabla\Phi|^2$.
Of course this discussion only holds for Dirac delta as weighting function, for others like Gaussian, the eigenvectors cannot be factored in this way.

\subsection{Second Order Regularizer}
The second order term uses ...
\begin{flalign}
\Rsecond(\flow) =\;&\int_\Omega\; \inf_{\aaux,\baux}\big[\;S_2(\flow,\aaux,\baux) +\beta*S_\text{aux}(\aaux,\baux)\;\big] \;d\x
&&\\
S_2(\flow,\aaux,\baux) =\;& \peronamalik\Big( (\ev_1\T(\nabla u-\aaux))^2 + (\ev_1\T(\nabla v-\baux))^2 \Big)
&&\\
+\;&\charbonnier\Big( (\ev_2\T(\nabla u-\aaux))^2 + (\ev_2\T(\nabla v-\baux))^2 \Big)
\nonumber&&\\
S_\text{aux}(\aaux,\baux) =\;& \peronamalik\Big(\sum\nolimits_{k=1}^2\;(\ev_k\T \jacob_{\aaux}\;\ev_1)^2 + (\ev_k\T \jacob_{\baux}\;\ev_1)^2  \Big)
&&\\
+\;&\charbonnier\Big(\sum\nolimits_{k=1}^2\;(\ev_k\T \jacob_{\aaux}\;\ev_2)^2 + (\ev_k\T \jacob_{\baux}\;\ev_2)^2  \Big)
\nonumber&&
\end{flalign}
